Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-04-19 paper-webserver.tex
EDIT: prefer the e+ scaling

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/o157vo26_amrgenes}
\end{center}
\caption{
% This needs to be specific to the image we are showing eg. the O157 vs. O26 comparison. We mention the general comparison in the text, and this can be offered as a specific example of that.
\textit{E. coli} genomes of serotype O157 (903) compared against genome of serotype O26 (291), for statistically significant differences in the carriage of 129 AMR genes. Fisher's Exact Test is used by Spfy for these comparisons.}
\label{fig-groupings}
\end{figure}

>>>>

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/o157vo26_amrgenes}
\end{center}
\caption{
% This needs to be specific to the image we are showing eg. the O157 vs. O26 comparison. We mention the general comparison in the text, and this can be offered as a specific example of that.
\textit{E. coli} genomes of serotype O157 (903 genomes) compared against genome of serotype O26 (291 genomes), for statistically significant differences in the carriage of 129 AMR genes. Fisher's Exact Test is used by Spfy for these comparisons.}
\label{fig-groupings}
\end{figure}
